---
title: "Regression"
author: "POLI3148 Group"
date: "2023-12-01"
output:
  html_document:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

#Default

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#Input

##Libraries:

```{r}
library(tidyverse)
library(readxl)
```

##Read in independent variables and get a summary:

```{r}
Dem_index <- read.csv("data/vdem_1984_2022_index.csv")
View(Dem_index)
summary(Dem_index)
```

##Read in dependent variables and ensure correct type for variables:

```{r}
Edu_as_of_G <- read_excel("data/Expenditure_on_Education_as_of_Total_Government_Expenditure.xlsx", col_types = c("guess", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric"))
View(Edu_as_of_G)

G_as_of_Y <- read_excel("data/Government_Expenditure_as_of_GDP.xlsx",  col_types = c("guess", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric", "numeric"))
View(G_as_of_Y)
```

#Data Wrangling

##Independent variable(s): Dem_index

###Libraries:

```{r}
library(dplyr)
```

###Rename:

```{r}
Dem_index <-
  Dem_index |>
  rename(Electoral = v2x_polyarchy, Liberal = v2x_libdem, Participatory = v2x_partipdem, Deliberative = v2x_delibdem, Egalitarian = v2x_egaldem) |>
  rename(Country = country_name, Year = year)
```

###Get necessary data:

```{r}
Dem_index_cleaned <-
  Dem_index |>
  select(Country, Year, Electoral, Liberal, Participatory, Deliberative, Egalitarian) |>
  filter(Year > 2013, Year < 2020)
View(Dem_index_cleaned)
```

###Sort the data into different tables:

```{r}
Dem_Electoral <-
  Dem_index_cleaned |>
  select(Country, Year, Electoral) |>
  pivot_wider(names_from = Year, values_from = Electoral) |>
  arrange(Country) |>
  rename(Twenty_fourteen = 2, Twenty_fifteen = 3, Twenty_sixteen = 4, Twenty_seventeen = 5, Twenty_eighteen = 6, Twenty_nineteen = 7)

Dem_Liberal <-
  Dem_index_cleaned |>
  select(Country, Year, Liberal) |>
  pivot_wider(names_from = Year, values_from = Liberal) |>
  arrange(Country) |>
  rename(Twenty_fourteen = 2, Twenty_fifteen = 3, Twenty_sixteen = 4, Twenty_seventeen = 5, Twenty_eighteen = 6, Twenty_nineteen = 7)

Dem_Participatory <-
  Dem_index_cleaned |>
  select(Country, Year, Participatory) |>
  pivot_wider(names_from = Year, values_from = Participatory) |>
  arrange(Country) |>
  rename(Twenty_fourteen = 2, Twenty_fifteen = 3, Twenty_sixteen = 4, Twenty_seventeen = 5, Twenty_eighteen = 6, Twenty_nineteen = 7)

Dem_Deliberative <-
  Dem_index_cleaned |>
  select(Country, Year, Deliberative) |>
  pivot_wider(names_from = Year, values_from = Deliberative) |>
  arrange(Country) |>
  rename(Twenty_fourteen = 2, Twenty_fifteen = 3, Twenty_sixteen = 4, Twenty_seventeen = 5, Twenty_eighteen = 6, Twenty_nineteen = 7)

Dem_Egalitarian <-
  Dem_index_cleaned |>
  select(Country, Year, Egalitarian) |>
  pivot_wider(names_from = Year, values_from = Egalitarian) |>
  arrange(Country) |>
  rename(Twenty_fourteen = 2, Twenty_fifteen = 3, Twenty_sixteen = 4, Twenty_seventeen = 5, Twenty_eighteen = 6, Twenty_nineteen = 7)
```

##Dependent variables: Edu_as_of_G, G_as_of_Y

###Arrange Edu_as_of_G:

####Rename:

```{r}
Edu_as_of_G <-
  Edu_as_of_G |>
  rename(Country = ...1)
```

####Sort out unwanted data:

```{r}
Edu_as_of_G_cleaned <-
  Edu_as_of_G |>
  select(Country, 3, 4, 5, 6, 7, 8) |>
  rename(Twenty_fourteen = 2, Twenty_fifteen = 3, Twenty_sixteen = 4, Twenty_seventeen = 5, Twenty_eighteen = 6, Twenty_nineteen = 7)
```

###Arrange G_as_of_Edu:

####Rename:

```{r}
G_as_of_Y <-
  G_as_of_Y |>
  rename(Country = ...1)
```

####Sort out unwanted data:

```{r}
G_as_of_Y_cleaned <-
  G_as_of_Y |>
  select(Country, 3, 4, 5, 6, 7, 8) |>
  rename(Twenty_fourteen = 2, Twenty_fifteen = 3, Twenty_sixteen = 4, Twenty_seventeen = 5, Twenty_eighteen = 6, Twenty_nineteen = 7)
```

#Data Analysis

##Join the variables from both sides

###Use G_as_of_Y and Dem_Electoral of the Year 2014 as an example:

```{r}
G_as_of_Y_cleaned_test <-
  G_as_of_Y_cleaned |>
  mutate(Country_t = Country, Year_t_x = Twenty_fourteen) |>
  select(Country_t, Year_t_x) 

Dem_Electoral_test <-
  Dem_Electoral |>
  mutate(Country_t = Country, Year_t_y = Twenty_fourteen) |>
  select(Country_t, Year_t_y)

Test1 <- 
  full_join(G_as_of_Y_cleaned_test, Dem_Electoral_test)

##VERY IMPORTANT NOTE: Our dataset lacks too much percentage of data:

is.na(Test1) |> sum()

##ONE POSSIBLE SOLUTION: Use data from 2014-2019 as a whole to avoid lack in data.
##ONE STRONG OBJECTION: The availability of data is still not changed.
```

###Another attempt (Edu_as_of_G and Dem_Electoral of the Year 2014):

```{r}
Edu_as_of_G_cleaned_test <-
  Edu_as_of_G_cleaned |>
  mutate(Country_t = Country, Year_t_x = Twenty_fourteen) |>
  select(Country_t, Year_t_x) 

Dem_Electoral_test <-
  Dem_Electoral |>
  mutate(Country_t = Country, Year_t_y = Twenty_fourteen) |>
  select(Country_t, Year_t_y)

Test2 <- 
  full_join(Edu_as_of_G_cleaned_test, Dem_Electoral_test)
```

##Find numerical correlations

```{r}

#Example cont`d: Find numerical correlations: (This part has not been finished)

#model <- lm(Year_t_y ~ Year_t_x, data = Test)
#view(model)
```

#Data Visualization

```{r}

theme_set(theme_bw())
#NOT CORRECT: library(ggplot)

#Example cont`d: Plot a graph:

Test1 |> 
  ggplot(aes(x = Year_t_x, y = Year_t_y)) + 
  geom_point() + 
  labs(x = "Government expenditure as of GDP", y = "Electoral Democracy Index", 
       title = "Government expenditure as of GDP and Electoral Democracy Level (2014)",
       caption = "By Yueling Xu, Data source: V-Dem v.13, Word Bank")

Test2 |> 
  ggplot(aes(x = Year_t_x, y = Year_t_y)) + 
  geom_point() + 
  labs(x = "Education expenditure as of government expenditure", y = "Electoral Democracy Index", 
       title = "Education expenditure as of government expenditure and Electoral Democracy Level (2014)",
       caption = "By Yueling Xu, Data source: V-Dem v.13, Word Bank")
```
